Learning Libraries of Subroutines for Neurally--Guided Bayesian Program Learning

### 2018-05-17 nips_2018.tex
consistent is-nil/nil usage

  \begin{tabular}{l}
    % $f_0($\code{r}$,\ell) \,=\, $\code{(fold $\ell$ r ($\lambda$ (x a)}\\
    % \phantom{$f_0($\code{r}$,\ell) \,=\, $\code{(fold}}\code{(cons (index (length a) $\ell$) a)))}\\
      % \hspace{0.5cm}($f_1$: \emph{Get the largest number})\\
    % $f_0(\ell) \,=\, $\code{(foldr $\ell$ 0 ($\lambda$ (x a)}\\\hspace{0.8cm}\code{ (if (> a x) a x)))}\\
      % \hspace{0.5cm}($f_1$: \emph{Get the largest number in $\ell$})\\
    %NOTE: this is the actual invention, but I removed a redundant lambda
    % below: $f_0(\ell,$\code{r}$) \,=\, $\code{(foldr r $\ell$ ($\lambda$ (x a) (cons x a)))}\\
    $f_0(\ell,$\code{r}$) \,=\, $\code{(foldr r $\ell$ cons)}\\
    \vspace{2ex}
      \hspace{0.5cm}($f_0$: \emph{Concatenate }\code{r}\emph{ with $\ell$})\\
    $f_1(\ell,$\code{k}$) \,=\, $\code{($f_0$ (cons k empty) $\ell$)}\\
    \vspace{2ex}
      \hspace{0.5cm}($f_1$: \emph{Append }\code{k}\emph{ to $\ell$})\\
    $f_2(\ell,$\code{k}$) \,=\, $\code{(foldr $\ell$ (empty$?$ $\ell$)}\\
    \phantom{$f_1(\ell,$\code{k}}
    \code{($\lambda$ (x a) (if a a (= k x))))}\\
      \hspace{0.5cm}($f_2$: \emph{Whether $\ell$ contains }\code{k})\\
  \end{tabular}&

  \begin{tabular}{l}
          $f_0($\code{s}$,$\code{a}$,$\code{b}$) \,=\, $\code{(map ($\lambda$ (x)}\\\hspace{1cm}\code{ (if (= x a) b x)) s)}\\
      \hspace{0.5cm}($f_0$: \emph{Performs character substitution)}\\
      $f_1($\code{s}$,$\code{c}$) \,=\, $\code{(foldr s s ($\lambda$ (x a)}\\\hspace{1.1cm}\code{ (cdr (if (= c x) s a))))}\\
        \hspace{0.5cm}($f_1$: \emph{Drop characters from }\code{s}\emph{ until  }\code{c}\emph{ reached})\\
      $f_2($\code{s}$) \,=\, $\code{(unfold s empty$?$ car }\\\hspace{1cm}\code{($\lambda$ (z) (}$f_1$\code{ z \codechar{ })))}\\
        \hspace{0.5cm}($f_2$: \emph{Abbreviates a sequence of words})\\
    \end{tabular}&

@@

\begin{table}[t]
  \centering
    \begin{tabular}{l}
      \toprule
      $f_0($\code{s}$,$\code{a}$,$\code{b}$) \,=\, $\code{(map ($\lambda$ (x) (if (= x a) b x)) s)}\\
      \hspace{0.5cm}($f_0$: \emph{Performs character substitution)}\\
      $f_1($\code{s}$,$\code{c}$) \,=\, $\code{(foldr s s ($\lambda$ (x a) (cdr (if (= c x) s a))))}\\
        \hspace{0.5cm}($f_1$: \emph{Drop first characters from }\code{s}\emph{ until  }\code{c}\emph{ reached})\\
      $f_2($\code{s}$) \,=\, $\code{(unfold s empty? car ($\lambda$ (z) (}$f_1$\code{ z SPACE)))}\\
        \hspace{0.5cm}($f_2$: \emph{Abbreviates a sequence of words. See Fig.~\ref{initialExampleDSL}})\\
        $f_3($\code{s}$,$\code{c}$) \,=\, $\code{(foldr s s ($\lambda$ (x a) (if (= c x) nil (cons x a))))}\\
        \hspace{0.5cm}($f_3$: \emph{Take characters from }\code{s}\emph{ until }\code{c}\emph{ reached)}
        %($\lambda$ ($\lambda$ (fold $0 $0 ($\lambda$ ($\lambda$ (if (char-eq? $1 $3) empty (cons $1 $0)))))))
  \\\bottomrule
    \end{tabular}
  \caption{Some text editing learned subroutines }\label{textPrimitives}
  \end{table}

>>>>

  \begin{tabular}{l}
    % $f_0($\code{r}$,\ell) \,=\, $\code{(fold $\ell$ r ($\lambda$ (x a)}\\
    % \phantom{$f_0($\code{r}$,\ell) \,=\, $\code{(fold}}\code{(cons (index (length a) $\ell$) a)))}\\
      % \hspace{0.5cm}($f_1$: \emph{Get the largest number})\\
    % $f_0(\ell) \,=\, $\code{(foldr $\ell$ 0 ($\lambda$ (x a)}\\\hspace{0.8cm}\code{ (if (> a x) a x)))}\\
      % \hspace{0.5cm}($f_1$: \emph{Get the largest number in $\ell$})\\
    %NOTE: this is the actual invention, but I removed a redundant lambda
    % below: $f_0(\ell,$\code{r}$) \,=\, $\code{(foldr r $\ell$ ($\lambda$ (x a) (cons x a)))}\\
    $f_0(\ell,$\code{r}$) \,=\, $\code{(foldr r $\ell$ cons)}\\
    \vspace{2ex}
      \hspace{0.5cm}($f_0$: \emph{Concatenate }\code{r}\emph{ with $\ell$})\\
    $f_1(\ell,$\code{k}$) \,=\, $\code{($f_0$ (cons k nil) $\ell$)}\\
    \vspace{2ex}
      \hspace{0.5cm}($f_1$: \emph{Append }\code{k}\emph{ to $\ell$})\\
    $f_2(\ell,$\code{k}$) \,=\, $\code{(foldr $\ell$ (is-nil $\ell$)}\\
    \phantom{$f_1(\ell,$\code{k}}
    \code{($\lambda$ (x a) (if a a (= k x))))}\\
      \hspace{0.5cm}($f_2$: \emph{Whether $\ell$ contains }\code{k})\\
  \end{tabular}&

  \begin{tabular}{l}
          $f_0($\code{s}$,$\code{a}$,$\code{b}$) \,=\, $\code{(map ($\lambda$ (x)}\\\hspace{1cm}\code{ (if (= x a) b x)) s)}\\
      \hspace{0.5cm}($f_0$: \emph{Performs character substitution)}\\
      $f_1($\code{s}$,$\code{c}$) \,=\, $\code{(foldr s s ($\lambda$ (x a)}\\\hspace{1.1cm}\code{ (cdr (if (= c x) s a))))}\\
        \hspace{0.5cm}($f_1$: \emph{Drop characters from }\code{s}\emph{ until  }\code{c}\emph{ reached})\\
      $f_2($\code{s}$) \,=\, $\code{(unfold s is-nil car }\\\hspace{1cm}\code{($\lambda$ (z) (}$f_1$\code{ z \codechar{ })))}\\
        \hspace{0.5cm}($f_2$: \emph{Abbreviates a sequence of words})\\
    \end{tabular}&

@@

\begin{table}[t]
  \centering
    \begin{tabular}{l}
      \toprule
      $f_0($\code{s}$,$\code{a}$,$\code{b}$) \,=\, $\code{(map ($\lambda$ (x) (if (= x a) b x)) s)}\\
      \hspace{0.5cm}($f_0$: \emph{Performs character substitution)}\\
      $f_1($\code{s}$,$\code{c}$) \,=\, $\code{(foldr s s ($\lambda$ (x a) (cdr (if (= c x) s a))))}\\
        \hspace{0.5cm}($f_1$: \emph{Drop first characters from }\code{s}\emph{ until  }\code{c}\emph{ reached})\\
      $f_2($\code{s}$) \,=\, $\code{(unfold s is-nil car ($\lambda$ (z) (}$f_1$\code{ z SPACE)))}\\
        \hspace{0.5cm}($f_2$: \emph{Abbreviates a sequence of words. See Fig.~\ref{initialExampleDSL}})\\
        $f_3($\code{s}$,$\code{c}$) \,=\, $\code{(foldr s s ($\lambda$ (x a) (if (= c x) nil (cons x a))))}\\
        \hspace{0.5cm}($f_3$: \emph{Take characters from }\code{s}\emph{ until }\code{c}\emph{ reached)}
        %($\lambda$ ($\lambda$ (fold $0 $0 ($\lambda$ ($\lambda$ (if (char-eq? $1 $3) nil (cons $1 $0)))))))
  \\\bottomrule
    \end{tabular}
  \caption{Some text editing learned subroutines }\label{textPrimitives}
  \end{table}
